---
title: "SphericalEllipse"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SphericalEllipse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SphericalEllipse)
library(geosphere)
```

Calculate points on a spherical ellipse with foci (140E, 45S) and (143E, 40S) for which the sum of 
the distances from the foci to any point on the ellipse is 900km 
```{r}
p1 <- c(140,-45)
p2 <- c(143,-40)
ps <- sphericalEllipse(p1,p2,900000)
plot(ps,type="l",xlab="Lon",ylab="Lat")
points(rbind(p1,p2),col="red",pch=16)
```

The combined distance to the foci from each point on the ellipse is
```{r}
distCosine(ps,p1)+distCosine(ps,p2)
```

The first and last point repeat to close the polygon
```{r}
ps[1,]==ps[nrow(ps),]
```


Calculate points on an ellipsoidal ellipse with foci (140E, 45S) and (143E, 40S) for which the sum of 
the distances from the foci to any point on the ellipse is 900km 
```{r}
p1 <- c(140,-45)
p2 <- c(143,-40)
ps <- ellipsoidalEllipse(p1,p2,900000)
plot(ps,type="l",xlab="Lon",ylab="Lat")
points(rbind(p1,p2),col="red",pch=16)
```

The combined distance to the foci from each point on the ellipse is
```{r}
distGeo(ps,p1)+distGeo(ps,p2)
```

The first and last point repeat to close the polygon
```{r}
ps[1,]==ps[nrow(ps),]
```



Construct several n-ellipses for three focal points
```{r}
p1 <- c(140,-45)
p2 <- c(143,-40)
p3 <- c(138,-43)
plot(rbind(p1,p2,p3),
     xlab="Lon",ylab="Lat",xlim=c(135,145),ylim=c(-47,-38),
     pch=16,col="red")
points(t(sphericalCentroid(rbind(p1,p2,p3))),pch=16,col="blue")
ps <- ellipsoidalNEllipse(rbind(p1,p2,p3),1400000)
points(ps,type="l")
ps <- ellipsoidalNEllipse(rbind(p1,p2,p3),1000000)
lines(ps,type="l")
ps <- ellipsoidalNEllipse(rbind(p1,p2,p3),800000)
lines(ps,type="l")
```

